Reliable analytic approximation of pseudo-$\cl$ covariances

### 2019-05-18 draft/paper.tex
slightly improve explanation row plot
added paragraph about the full 2-bins cov

\begin{itemize}
\item Naive Covariance
  \begin{equation}
    C^{abcd} = \frac{\pcl{l}ad \pcl{l}bc + \pcl{l}ac \pcl{l}bd}{f_{sky} (2l +
      1) \Delta l} \delta_{ll'}
  \end{equation}
\item Approximation 1
\item Approximation 2
\end{itemize}

@@

In this sense, one can see in Fig.~\ref{fig:TTTT_EEEE_chi2} that, we fully
recover the $\chi^2$ distribution (defining $\chi^2 = \cl - \langle \cl
\rangle C^{-1} \cl - \langle \cl \rangle$) for the TTTT case; whereas for the
worst case (i.e. EEEE) we are able to recover its shape, although sifted
toward lower values. This might be consequence of the fact that the inverse of
the covariance matrix is biased. It is interesting to note that even
the approximation of the mixing matrix as that of the case with spin 0, gives
good results. The eigenvalues of the covariance matrix
(Fig.~\ref{fig:TTTT_EEEE_eigv}) are also recovered within the 1\%, for all
scales in the TTTT case, and for the smaller scales in the EEEE case. Finally,
the analytical approximations are shown to describe the scale coupling (see
Fig.~\ref{fig:TTTT_rows} that comes from the fact we are masking some regions
of the sky.

@@

>>>>

\begin{itemize}
\item Naive Covariance
  \begin{equation}
    C^{abcd} = \frac{\pcl{l}ad \pcl{l}bc + \pcl{l}ac \pcl{l}bd}{f_{sky} (2l +
      1) \Delta l} \delta_{ll'}
    \label{eq:naive}
  \end{equation}
\item Approximation 1
\item Approximation 2
\end{itemize}

@@

In this sense, one can see in Fig.~\ref{fig:TTTT_EEEE_chi2} that, we fully
recover the $\chi^2$ distribution (defining $\chi^2 = \cl - \langle \cl
\rangle C^{-1} \cl - \langle \cl \rangle$) for the TTTT case; whereas for the
worst case (i.e. EEEE) we are able to recover its shape, although sifted
toward lower values. This might be consequence of the fact that the inverse of
the covariance matrix is biased. It is interesting to note that even
the approximation of the mixing matrix as that of the case with spin 0, gives
good results. The eigenvalues of the covariance matrix
(Fig.~\ref{fig:TTTT_EEEE_eigv}) are also recovered within the 1\%, for all
scales in the TTTT case, and for the smaller scales in the EEEE case. Finally,
the analytical approximations are shown to describe the scale coupling (see
Fig.~\ref{fig:TTTT_rows} that comes from the fact we are masking some regions
of the sky. The larger relative deviation for the better approximations are
due to the fact that there is a division by $0$, while for the naive
approximation, which is defined diagonal (see Eq.~\ref{eq:naive}), the
relative deviation is exactly $-1$ for all values with $l \neq l'$.

@@

Finally, the analytical covariance also works for 2-bin correlations. The
$\chi^2$ distribution for the covariance matrix of the modes TT, TE and EE
among two bins is shown in Fig.~\ref{fig:TTTEEE_chi2}. The eigenvalues
are recovered well except for the lower ones that diverge up to $20\%$ (see
Fig.~\ref{fig:TTTEEE_eigv}, this is not translated to any substantial
difference in the correlation matrices (see Fig.~\ref{fig:TTTEEE_corr}).

\begin{figure} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_2b_same_mask_Efstathiou_TTTEEE_Full_chi2.png}
  \caption{$\chi^2$ distribution check for the full analytical covariance
    matrix for the modes TT, TE and EE among two bins.}
  \label{fig:TTTEEE_chi2}
\end{figure}

\begin{figure} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_2b_same_mask_Efstathiou_TTTEEE_Full_reldev_eigval.png}
  \caption{Relative difference between the analytical and simulations
    covariance matrix eigenvalues for the modes TT, TE and EE among two bins.}
  \label{fig:TTTEEE_eigv}
\end{figure}

\begin{figure} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_2b_same_mask_Efstathiou_TTTEEE_Full_correlation_difference.png}
  \caption{Difference of the correlation matrices of the simulated $\cl$ and
    the analytical one for the modes TT, TE and EE among two bins..}
  \label{fig:TTTEEE_corr}
\end{figure}
